---
title: "RMarkdown By example"
author: "Jake Kramer"
date: "May 5, 2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is a Header!

### The more # you put at the beginning of a line

#### The smaller the header text gets.

# You can use a single # but

## that is usually reserved for the title!

In general you would use

* sections: ## 
* sub-sections: ### 
* sub-sub-sections: #### etc

1. To make a numbered list, you just write a number and a period.
2. Remember, you just write a number and a period.
    - To make a sub list you need two-tabs or four spaces and a +
    - Or a -
    * or a *
    1. a number starts a numbered sublist
    1. Even if you use the same number, Markdown don't care, you get the next one anyway.
    4. And if you try to skip numbers, you STILL get the right one.
    + But, if you hop out of the numbering and back in...
    99. You can start at any number you want!
    a. You can do letters too.
    a. They behave the same way!
    1. Not respecting your choices.
        + How far can you nest? This is level 3.
            4. level 4!
                5. level 5...
                    6. level 6!?
                        + ...
                            + ...
                                + ...
                                    + ...
                                        + ...
                                            + ...
                                                + ...
                                                    + ...
                                                        + ...
                                                            + ...
                                                                + ...
                                                                                                + At least 18 levels, so that should be enough for *most* purposes.

That's enough lists... let's move on!

***

We can make a horizontal line with three asterisks ***

> and we can make a block quote with the greater-than symbol: >
Also note:
To put text on a new line...

You can emphasise *something* by putting it in the middle of two asterisks, and if you're feeling **bold** put something in the middle of four asterisks. don't put ***anything*** in the middle of six asterisks that's just overdoing it!

For 
the
most
part
R doesn't care
about you
putting line
breaks in 
wherever you want.
Nor                                     does                                  R                     care
about                                   horizontal                            whitespace            (unless you're making nested lists.)

One exception to that is if you put two spaces  
at the end of a line then press enter. Note that this is different than pressing enter twice

at the end of a line. See the gap between the text that pressing enter twice

at the end of a line makes that two spaces  
at the end of a line doesn't?

***

Tables | are | easy | to | make
-------|-----|------|----|------
We| just| divide| the| cells
with| vertical| bars.| Easy, | right?

You | don't | need | to | use | a | specific| number
-|--|---|----|-----|------|--------|---------|
of| horizontal | dashes | ---- | in | each| column | to
make | a | table.|||||

You | can | also | align
:-|-:|:-:|-|
columns| how | you | like
right aligned text here. | left aligned text here. | centered text here. | plain old default here.
:-| -:| :-: | -

html comments look like this \<!-- comment goes in here --\>

<!-- if I don't escape it, you cant see it!-->

```{r}
# This is an R "code chunk", to create one you need three back-ticks (usually found on the same key as ~)
# you also need open and closing curly braces with a lower-case r inside.
# you close a code chunk with another three back ticks.
```

```{r}
# You shouldn't ever type one out though.
# hit ctrl+alt+i or cmd+option+i
# to create one automatically!
```

```{r}
# code chunks evaluate R code:
2 + 2
```
Then they display the output.

You can set options for the code chunk, the first we'll discuss is the chunk name.  
You put the name after the r inside the curly braces with no comma between them, like this: ```{r my code chunk}
```{r my code chunk}
# my code chunk here
x <- sample(1:10)
print(x)
```

Chunk names must be unique or your get errors ```{r my code chunk 2}
```{r my code chunk 2}
# my other code chunk here
y <- rnorm(10)
summary(y)
```

After the name you can put a comma and start adding options for how the chunk will be treated, eg: ```{r my code chunk 3, eval = FALSE}
```{r my code chunk 3, eval = FALSE}
# This chunk is displayed, but not ran.
y <- pi
print(y)
```
If we print y in another chunk after this one, it still has it's previous value!
```{r}
print(y)
```

On the other hand, sometimes we want our code to be ran and not seen (this looks nicer in a report you might do for work!), ```{r invisi-chunk, echo = FALSE} does this for us.

```{r invisi-chunk, echo = FALSE}
# This chunk is hidden, but it is run and produces output!
plot(cars$speed, cars$dist)
```

or

something like  ```{r stealth mode activated, echo = FALSE}
```{r stealth mode activated, echo = FALSE}
# This chunk is also hidden, but it is run and produces output!
tan(pi/8)
```

Now, you might notice the raw output from the chunks doesn't look great. I agree! So we can hide the chunk with the echo = FALSE argument, and instead of outputting from the chunk, we can store anything we do in an object, then output it in what is called inline mode.

In-line mode is started with a single backtick, and the letter r, followed by some r code, and closed with another backtick, like this: `` `r
some_r_code` ``. I had to do some black magic to get this to display correctly.

Here's an example of that at play:
```{r, echo = FALSE}
tanpi_8 <- tan(pi/8)
pi/8
```

The tangent of pi/8 = `r tanpi_8`.

There is also a "verbatim" mode which highlights text and doesn't evaluate special characters.

The first verbatim mode is in-line, single back-tick open and close: `my verbatim inline text`. This is useful for showing things like dollar signs `$` or other special characters like comments `<!-- see? -->`.

double ``ticks`` do the same thing as single, but they let you in-line verbatim single back ticks, see: `` a wild back-tick appears! --> ` `` 

Three back ticks, the same as making an R code chunk but without the {r}, creates a verbatim block
```
This is useful if you just want to write some code examples:
x <- 1
y <- 1
while the night is young do:
      z <- x + y
      swing your partner do si do

I didn't htink of this before, but this
    Might be an even better way to present your pseudocode
    Than doing it in a 
List
    Structure!
```

If you know LaTeX, you'll be happy to know you can use LaTeX-like syntax (MathJax) to do some typesetting.

A single `$` enters in-line math-mode and another `$` closes it. Like this: $\frac{\pi}{8} \approx 0.3927$

While a double `$$` enters equation math-mode and another`$$` closes it. Like this:  
$$\frac{\pi}{8} \approx 0.3927$$

You can even combine either math-mode and in-line R, like this: ``$$\tan\left(\frac{\pi}{8}\right) = `r
tan(pi/8)` $$ ``

$$\tan\left(\frac{\pi}{8}\right) = `r tan(pi/8)`$$

I hope you found this helpful!