---
title: "Stats 102A - Homework 4"
author: "Zooey Nguyen"
date: "3/17/2021"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("105195172_stats102a_hw4.R")
```

## Problem 1a

```{r}
a <- pqnumber(sign = 1, p = 3, q = 4, nums = 1:8)
b <- pqnumber(sign = 1, p = 6, q = 0, nums = c(3,9,5,1,4,1,3))
c <- pqnumber(sign = -1, p = 5, q = 1, nums = c(2,8,2,8,1,7,2))
is_pqnumber(a)
is_pqnumber(b)
is_pqnumber(c)
print(a)
print(b)
print(c)
as_pqnumber(3.14)
as_numeric(c)
```


## Problem 1b
The subtraction and multiplication functions are eluding me...
```{r}
print(pq_add(a, b))
cat("\n")
print(pq_add(a, c))
cat("\n")
print(pq_add(b, c))
```

## Problem 2
```{r}
b <- my_sqrt(5)
b^2
```
If we were to calculate an arbitrary root $n$ for the number $a$ we will be solving the root-finding problem for the equation $x^n - a$. In this case the iterative update becomes $x_{n+1} = x_n - \frac{x^n - a}{nx^{n-1}} = x - \frac{x}{n} + \frac{a}{nx^{n-1}}$.
```{r}
e <- my_root(7,n=5)
e^5
```
The first four iterations are found with verbose=TRUE:
5.600583 
4.481889 
3.588981 
2.879623 
Calculating $e_1 \to e_4$ is subtracting 1.475773 from each:
$e_1 = 4.12481$
$e_2 = 3.006116$
$e_3 = 2.113208$
$e_4 = 1.40385$
I calculated the ratio between these iterations and found that they slightly increased each time, meaning each iteration did relatively better than the last at squeezing in on the answer. 

